---
title: "boxgooglemap"
author: "Boxi Zhang, Priya Pullolickal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{boxgooglemap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

The boxgooglemap package is connected with the google geocode API to convert location and coordination by two function:
  
  
- address
- coord

**package httr is required to be installed** 
  
##Functions

###address
  
The 'address' function retrive the address of a given coordinate. The funtion uses the google geocode API to retrieve the result.

The input **latlong** is a character string that includes the latitude and the longitude.

The function returns a dataframe cointaining full address names as well as the coordinates:

```{r, fig.show='hold', message=FALSE}
library(boxgooglemap)
head(address("41.40450 76"), n = 5)
tail(address("67 115"), n = 5)

```


###coord
The 'coord' function is a function that provides the user with the coordinates of a given address. The function uses the google geocode API to retrieve the result.

Please input **address**, a character string that includes address components.

If the address has partial match, different locations with their full names and coordinates will be retrieved as a dataframe:
```{r, fig.show='hold', message=FALSE}
library(boxgooglemap)
coord("chang sha, china")

coord("milan")
```
